Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-03 paper_jasa.tex
included m in proof to theorem 3.1

{ \em proof}

@@

Thus expected power in equation \ref{power_exp} be
\begin{eqnarray*}
 Pr(p_{B} < p_0) &=& 1- Pr( p_0 \le p_{B} ) \\
  &=& 1- \int_{0}^{1}{Pr( p_0 \le p_{B} |p_{B} =t) f_{p_{B} }(t)dt } \\
  &=& 1-  \int_{0}^{1}{F{p_0}(t) f_{p_{B} }(t)dt }    \\
  & \rightarrow &1-  \int_{0}^{1}{ f_{p_{B} }(t)dt }  = F_{p_B}(0) \quad \text{as} \quad m \rightarrow \infty
\end{eqnarray*}

>>>>

\begin{proof}

@@

Thus expected power in equation \ref{power_exp} be
\begin{eqnarray*}
 Pr(p_{B} < p_0) &=& 1- Pr( p_0 \le p_{B} ) \\
  &=& 1- \int_{0}^{1}{Pr( p_0 \le p_{B} |p_{B} =t) f_{p_{B} }(t)dt } \\
  &=& 1-  \int_{0}^{1}{F{p_0}(t) f_{p_{B} }(t)dt }    \\
 &=& 1 - \int_{0}^{1}(t) f_{p_{B} }(t)dt + \int_{0}^{1} (1-t)^{m-1} f_{p_{B} }(t)dt \\
 &=& E\left[(1-p_B)^{m-1}\right] \\
%  & \rightarrow &1-  \int_{0}^{1}{ f_{p_{B} }(t)dt }  = F_{p_B}(0) \quad \text{as} \quad m \rightarrow \infty
\end{eqnarray*}
\end{proof}
